### 2024-07-22 NN/tables/backward.tex
commit

    \begin{table*}
        \centering
        \begin{tabular}{p{12cm}r}r}
\hline
\hline
 features                                                                                            &    R2 \\
\hline
 flow\_rate1,conc\_nano1,Kfluid1,heat\_flux1,X\_D1,flow\_rate2,conc\_nano2,Kfluid2,heat\_flux2,X\_D2 & 84.97 \\
 conc\_nano1,Kfluid1,heat\_flux1,X\_D1,flow\_rate2,conc\_nano2,Kfluid2,heat\_flux2,X\_D2             & 71.27 \\
 flow\_rate1,Kfluid1,heat\_flux1,X\_D1,flow\_rate2,conc\_nano2,Kfluid2,heat\_flux2,X\_D2             & 71.9  \\
 flow\_rate1,conc\_nano1,heat\_flux1,X\_D1,flow\_rate2,conc\_nano2,Kfluid2,heat\_flux2,X\_D2         & 73.44 \\
 flow\_rate1,conc\_nano1,Kfluid1,X\_D1,flow\_rate2,conc\_nano2,Kfluid2,heat\_flux2,X\_D2             & 74.25 \\
 flow\_rate1,conc\_nano1,Kfluid1,heat\_flux1,flow\_rate2,conc\_nano2,Kfluid2,heat\_flux2,X\_D2       & 70.58 \\
 flow\_rate1,conc\_nano1,Kfluid1,heat\_flux1,X\_D1,conc\_nano2,Kfluid2,heat\_flux2,X\_D2             & 81.67 \\
 flow\_rate1,conc\_nano1,Kfluid1,heat\_flux1,X\_D1,flow\_rate2,Kfluid2,heat\_flux2,X\_D2             & 40.24 \\
 flow\_rate1,conc\_nano1,Kfluid1,heat\_flux1,X\_D1,flow\_rate2,conc\_nano2,heat\_flux2,X\_D2         & 49.33 \\
 flow\_rate1,conc\_nano1,Kfluid1,heat\_flux1,X\_D1,flow\_rate2,conc\_nano2,Kfluid2,X\_D2             & 72.42 \\
 flow\_rate1,conc\_nano1,Kfluid1,heat\_flux1,X\_D1,flow\_rate2,conc\_nano2,Kfluid2,heat\_flux2       & 74.5  \\
\hline
\end{tabular}
\hline
        \caption{Results of Backward Feature Elimination}
        \label{backward}
    \end{table*}

>>>>

    \begin{table*}
        \centering
        \begin{tabular}{lr}
\hline
 features                                                                                                     &    R2 \\
\hline
 flow\_rate1, conc\_nano1, Kfluid1, heat\_flux1, X\_D1, flow\_rate2, conc\_nano2, Kfluid2, heat\_flux2, X\_D2 & 82.69 \\
 conc\_nano1, Kfluid1, heat\_flux1, X\_D1, flow\_rate2, conc\_nano2, Kfluid2, heat\_flux2, X\_D2              & 62.45 \\
 flow\_rate1, Kfluid1, heat\_flux1, X\_D1, flow\_rate2, conc\_nano2, Kfluid2, heat\_flux2, X\_D2              & 81.63 \\
 flow\_rate1, conc\_nano1, heat\_flux1, X\_D1, flow\_rate2, conc\_nano2, Kfluid2, heat\_flux2, X\_D2          & 73.64 \\
 flow\_rate1, conc\_nano1, Kfluid1, X\_D1, flow\_rate2, conc\_nano2, Kfluid2, heat\_flux2, X\_D2              & 72.94 \\
 flow\_rate1, conc\_nano1, Kfluid1, heat\_flux1, flow\_rate2, conc\_nano2, Kfluid2, heat\_flux2, X\_D2        & 67.45 \\
 flow\_rate1, conc\_nano1, Kfluid1, heat\_flux1, X\_D1, conc\_nano2, Kfluid2, heat\_flux2, X\_D2              & 68.03 \\
 flow\_rate1, conc\_nano1, Kfluid1, heat\_flux1, X\_D1, flow\_rate2, Kfluid2, heat\_flux2, X\_D2              & 76.57 \\
 flow\_rate1, conc\_nano1, Kfluid1, heat\_flux1, X\_D1, flow\_rate2, conc\_nano2, heat\_flux2, X\_D2          & 38.28 \\
 flow\_rate1, conc\_nano1, Kfluid1, heat\_flux1, X\_D1, flow\_rate2, conc\_nano2, Kfluid2, X\_D2              & 69.39 \\
 flow\_rate1, conc\_nano1, Kfluid1, heat\_flux1, X\_D1, flow\_rate2, conc\_nano2, Kfluid2, heat\_flux2        & 81.61 \\
\hline
\end{tabular}
        \caption{Results of Backward Feature Elimination}
        \label{backward}
    \end{table*}

### 2024-07-22 NN/tables/forward.tex
commit

    \begin{table*}
        \centering
        \begin{tabular}{lr}
\hline
 features                                                      &    R2 \\
\hline
 X\_D1                                                         & 15.01 \\
 flow\_rate2                                                   & 34.3  \\
 conc\_nano2                                                   & 10.78 \\
 Kfluid2                                                       & 49.29 \\
 heat\_flux2                                                   & -8.26 \\
 flow\_rate1,Kfluid2                                           & 52.94 \\
 conc\_nano1,Kfluid2                                           & 50.8  \\
 Kfluid1,Kfluid2                                               & 47.57 \\
 heat\_flux1,Kfluid2                                           & 52.31 \\
 X\_D1,Kfluid2                                                 & 62.32 \\
 flow\_rate2,Kfluid2                                           & 29.14 \\
 conc\_nano2,Kfluid2                                           & 61.05 \\
 heat\_flux2,Kfluid2                                           & 66.61 \\
 X\_D2,Kfluid2                                                 & 53.44 \\
 flow\_rate1,Kfluid2,heat\_flux2                               & 60.58 \\
 conc\_nano1,Kfluid2,heat\_flux2                               & 61.96 \\
 Kfluid1,Kfluid2,heat\_flux2                                   & 66.64 \\
 heat\_flux1,Kfluid2,heat\_flux2                               & 42.41 \\
 X\_D1,Kfluid2,heat\_flux2                                     & 66.55 \\
 flow\_rate2,Kfluid2,heat\_flux2                               & 55.24 \\
 conc\_nano2,Kfluid2,heat\_flux2                               & 67.09 \\
 X\_D2,Kfluid2,heat\_flux2                                     & 68.58 \\
 flow\_rate1,Kfluid2,heat\_flux2,X\_D2                         & 90.12 \\
 conc\_nano1,Kfluid2,heat\_flux2,X\_D2                         & 78.64 \\
 Kfluid1,Kfluid2,heat\_flux2,X\_D2                             & 88.23 \\
 heat\_flux1,Kfluid2,heat\_flux2,X\_D2                         & 49.47 \\
 X\_D1,Kfluid2,heat\_flux2,X\_D2                               & 79.9  \\
 flow\_rate2,Kfluid2,heat\_flux2,X\_D2                         & -0.88 \\
 conc\_nano2,Kfluid2,heat\_flux2,X\_D2                         & 63.17 \\
 conc\_nano1,Kfluid2,heat\_flux2,X\_D2,flow\_rate1             & 95.97 \\
 Kfluid1,Kfluid2,heat\_flux2,X\_D2,flow\_rate1                 & 76.54 \\
 heat\_flux1,Kfluid2,heat\_flux2,X\_D2,flow\_rate1             & 60.12 \\
 X\_D1,Kfluid2,heat\_flux2,X\_D2,flow\_rate1                   & 80.67 \\
 flow\_rate2,Kfluid2,heat\_flux2,X\_D2,flow\_rate1             & 68.87 \\
 conc\_nano2,Kfluid2,heat\_flux2,X\_D2,flow\_rate1             & 68.35 \\
 Kfluid1,Kfluid2,heat\_flux2,X\_D2,flow\_rate1,conc\_nano1     & 80.62 \\
 heat\_flux1,Kfluid2,heat\_flux2,X\_D2,flow\_rate1,conc\_nano1 & 67.03 \\
 X\_D1,Kfluid2,heat\_flux2,X\_D2,flow\_rate1,conc\_nano1       & 85.73 \\
 flow\_rate2,Kfluid2,heat\_flux2,X\_D2,flow\_rate1,conc\_nano1 & 75.7  \\
 conc\_nano2,Kfluid2,heat\_flux2,X\_D2,flow\_rate1,conc\_nano1 & 78.99 \\
\hline
\end{tabular}
        \caption{Results of Forward Feature Selection for different features}
        \label{forward}
    \end{table*}

>>>>

    \begin{table*}
        \centering
        \begin{tabular}{lr}
\hline
 features                                                             &    R2 \\
\hline
 X\_D1                                                                & 14.85 \\
 flow\_rate2                                                          & 27.69 \\
 conc\_nano2                                                          & 11.15 \\
 Kfluid2                                                              & 62.66 \\
 heat\_flux2                                                          & -4.92 \\
 flow\_rate1, Kfluid2                                                 & 75.33 \\
 conc\_nano1, Kfluid2                                                 & 64.49 \\
 Kfluid1, Kfluid2                                                     & 67.9  \\
 heat\_flux1, Kfluid2                                                 & 74.3  \\
 X\_D1, Kfluid2                                                       & 67.3  \\
 flow\_rate2, Kfluid2                                                 &  9.94 \\
 conc\_nano2, Kfluid2                                                 & 87.59 \\
 heat\_flux2, Kfluid2                                                 & 56.8  \\
 X\_D2, Kfluid2                                                       & 67.59 \\
 flow\_rate1, Kfluid2, conc\_nano2                                    & 60.42 \\
 conc\_nano1, Kfluid2, conc\_nano2                                    & 78.36 \\
 Kfluid1, Kfluid2, conc\_nano2                                        & 79.88 \\
 heat\_flux1, Kfluid2, conc\_nano2                                    & 90.37 \\
 X\_D1, Kfluid2, conc\_nano2                                          & 84.51 \\
 flow\_rate2, Kfluid2, conc\_nano2                                    & 65.14 \\
 heat\_flux2, Kfluid2, conc\_nano2                                    & 57.1  \\
 X\_D2, Kfluid2, conc\_nano2                                          & 54.6  \\
 flow\_rate1, Kfluid2, conc\_nano2, heat\_flux1                       & 62.62 \\
 conc\_nano1, Kfluid2, conc\_nano2, heat\_flux1                       & 92.87 \\
 Kfluid1, Kfluid2, conc\_nano2, heat\_flux1                           & 80.94 \\
 X\_D1, Kfluid2, conc\_nano2, heat\_flux1                             & 87.63 \\
 flow\_rate2, Kfluid2, conc\_nano2, heat\_flux1                       & 82.76 \\
 heat\_flux2, Kfluid2, conc\_nano2, heat\_flux1                       & 55.75 \\
 X\_D2, Kfluid2, conc\_nano2, heat\_flux1                             & 75.43 \\
 flow\_rate1, Kfluid2, conc\_nano2, heat\_flux1, conc\_nano1          & 49.56 \\
 Kfluid1, Kfluid2, conc\_nano2, heat\_flux1, conc\_nano1              & 93.06 \\
 X\_D1, Kfluid2, conc\_nano2, heat\_flux1, conc\_nano1                & 87.49 \\
 flow\_rate2, Kfluid2, conc\_nano2, heat\_flux1, conc\_nano1          & 69.35 \\
 heat\_flux2, Kfluid2, conc\_nano2, heat\_flux1, conc\_nano1          & 65.5  \\
 X\_D2, Kfluid2, conc\_nano2, heat\_flux1, conc\_nano1                & 64.18 \\
 flow\_rate1, Kfluid2, conc\_nano2, heat\_flux1, conc\_nano1, Kfluid1 & 84.19 \\
 X\_D1, Kfluid2, conc\_nano2, heat\_flux1, conc\_nano1, Kfluid1       & 87.54 \\
 flow\_rate2, Kfluid2, conc\_nano2, heat\_flux1, conc\_nano1, Kfluid1 & 76.61 \\
 heat\_flux2, Kfluid2, conc\_nano2, heat\_flux1, conc\_nano1, Kfluid1 & 71.81 \\
 X\_D2, Kfluid2, conc\_nano2, heat\_flux1, conc\_nano1, Kfluid1       & 77.34 \\
\hline
\end{tabular}
        \caption{Results of Forward Feature Selection for different features}
        \label{forward}
    \end{table*}
